---
title: "P8105: Homework 1"
author: "Sydney Musick (sm4993)"
date: 9/29/21
output: github_document
---

# Problem 1

### Loading in the tidyverse library.
```{r}
library(tidyverse)
```

### Creating the data frame and finding the means of the variables.
```{r df_create}
set.seed(1000)

q1_df = tibble(
  random_sample = rnorm(10),
  vec_pos = random_sample > 0,
  vec_character = c("New York", "Michigan", "Florida", "Texas", "Georgia", "California", "Washington", "Colorado", "Utah", "Nevada"), 
  vec_factor = factor(c("rain", "sun", "snow", "snow", "snow", "rain", "sun", "sun", "sun", "snow"))
)

mean_random_sample = mean(pull(q1_df, random_sample))
mean_vec_pos = mean(pull(q1_df, vec_pos))
mean_vec_character = mean(pull(q1_df, vec_character))
mean_vec_factor = mean(pull(q1_df, vec_factor))
```
Using this code, we can take the means of `random_sample` and of `vec_positive`, but not of `vec_character` or `vec_factor`.


### Taking the means of `vec_character` and `vec_factor` using the `as.numeric` function.
```{r results = FALSE}
as.numeric(pull(q1_df, vec_character))
as.numeric(pull(q1_df, vec_factor))
```
Using this code, we were able to take the mean of `vec_factor` but not of `vec_character`. This occurs because, using `as.numeric`, we are able to convert the factor variable to integers by numbering the different factor "levels". The character variable wasn't able to be converted because there is no order or logic to the observations within that variable. This explains the results we get when we take the means of these variables. 